% ************************** Thesis Acknowledgements **************************

%\begin{acknowledgements}      


%And I would like to acknowledge ...


%\end{acknowledgements}
\chapter{Acknowledgements}

I have never been one for effusive speaches or declarations, it makes me feel akward, but after almost 4 years working for my PhD there are many acknowledgements I would like to make. However I will keep this section quite brief.
I would like to thank Valerie Gibson for giving me the oportunity to complete a PhD at the Univerisyt of Cambridge, and for her guideance throughout my research and the repeated reading of this dissertation. %Also for her support whilst I spent much of my first two years at Cambridge training with Cambridge University Women's Boat Club. 
Marc-Olivier Bettler and Harry Cliff, without their support and encouragment my PhD would naver have ended and I would not have had the oportunity to work on one of the LHCb experiments flagship analyses.
The \bmumu LHCb analysis group, for the tireless effort that went into the \BF analysis and the guidance and support I recived for my work. I have benefited a huge from the experinence of those within this group. 
The Science and Technologies Facutlies Council for funding my research, enabling me to spend a year living in Geneva and travel to internatial conferences. Selwyn College for support throughout my PhD, particularly with respect to the finacial support and encouragement I received from the college during the time I spent rowing with Cambridge University Women's Boat Club. Whilst on the topic of rowing, I would like to thank again Valerie Gibson and Marc-Olivier Bettler for their support whilst I spent much of the first two years at Cambridge training for the Boat Races. 
Past and present members of the Cambridge HEP group, for the good friends I've made and making coffee and lunch breaks entertaining. Particular thanks go to John Hill and Steve Wotton for the computing infastructure I greatly benefited from during my PhD and for putting up with me filling up a lot of disk space. Also thanks go to Susan Haines for answering my dumb questions and giving me hope that everything would be ok. 
My friends at Crossroad Church Saint Genis-Pouilly, for giving me a home and support whilst I lived at CERN.
My friends from Oxford and Cambridge, rowing friends, church friends and physics friends. To list them all would take some time but special thanks go to Anouska Bartlett for volunteraily reading through my dissertation despite having no physics backgroud. 
Finally, I would like to thank my parents and my sister. Thank you for coping with me being very absent during my PhD, although you did move to the oposite side of the country! 

%Also, I would like to thank Val and Marco for their support whilst I spent much of my first two years at Cambridge training with Cambridge University Women's Boat Club. 

%I would like to thank the following for:
%\begin{itemize}
%\item Valerie Gibson, giving me the oportunity to do a PhD, guidance/support, repeated reading of this dissertation
%\item John Hill (special mention in Cambridge HEP group?) computing support and something about my batch jobs, though I wasn't as bad as Steve or Bono. Computational infastuction that made this work possible - filling up all of r02/r03.
%\item the Science and Technologies Facutlies Counci, for funding. Allowing me to actually do my PhD and also letting me live in Geneva (or close enough) for a year and exciting conference destinations
%\item Harry Cliff and Marc-Olivier Bettler, invaluable, pointing me in the right direction, answering stupid questions and their encouragement, patience whilst I was rowing (Support from Val and Marco about rowing, since most people are not)
%\item the \bmumu analysis group, (particulary name some??) tireless effort that went into the \BF analysis from which my work on the \el benefited and I have learnt a lot. Feedback and adivse on my work and my benefitting from their experince, for putting up with me
%\item LHCb collaboration - relied on collegeues both in cambridge and outside cambridge
%\item Cambridge HEP group, past and present memebers, the lunch and coffee group, listening to me complain or talk about rowing and telling me that everything will be ok in the end
%\item Selwyn College, for the support particulary the Sport Grant and rowing
%\item CUWBC for making my time at Cambridge something more than just physics
%\item CUCC for showing me ther is life after rowing
%\item Simon?
%\item Anouska - of she reads my work?
%\item my family for coping with me hardly visiting home for the last 4 years
%\item my friends i suppose, tbh you know who you are (mostly you are rowing friends!) For reminding me that what I do it pretty cool
%\item Crossroads SG for making my time at CERN great and giving me a home when I was far from the UK
%\item Dave Green for teaching
%\end{itemize}
